Harnessing the cloud to understand light: A whitepaper detailing the \MaxwellFDS core solver

### 2012-08-16 thesis.tex
small

\section{Harnessing Amazon's Elastic Compute Cloud} 
\subsection{Accessing }

>>>>

\section{Harnessing Amazon's Elastic Compute Cloud} 
In this section, we give an overview of how \MaxwellFDS utilizes
    the Amazon Elastic Compute Cloud service to 
    provide nearly unlimited scalability when running electromagnetic simulations.

\subsection{Reserving instances}
\subsection{Use of spot instances}
Talk about pricing and how one can be kicked off.

\subsection{Web console for manual monitoring/shutdown}
